---
title: "EPI 590 Final Project"
author: "Parth Trivedi"
format: html
echo: True
error: True
---

The data used for this project is a Pokemon dataset which includes names, types, health points, attack, defense, special attack, special defense, speed, what generation the pokemon are from, and whether they are classified as legendary. The dataset was retrieved from Kaggle.

## Loading Necessary Packages and Reading in Data

```{r}
library(here, gtsummary)

pokemon <- read.csv(here::here("Data/Pokemon.csv"))
```

## Creating and Saving Table of Descriptive Statistcs

```{r}
table1 <- gtsummary::tbl_summary(
						pokemon,
						by = "Type.1",
						include = c(HP, Attack, Defense, Sp..Atk, Sp..Def, Speed),
						label = list(
												 HP = "Health Points",
												 Sp..Atk = "Special Attack",
												 Sp..Def = "Special Defense")
						)

gtsummary::tbl_summary(
						pokemon,
						by = "Type.1",
						include = c(HP, Attack, Defense, Sp..Atk, Sp..Def, Speed),
						label = list(
												 HP = "Health Points",
												 Sp..Atk = "Special Attack",
												 Sp..Def = "Special Defense")
						)

gtsummary::inline_text(table1, variable = HP, column = Steel)

table1_save <- here("Data", "EPI590_Table1")
```

Table describing median, first quartile, and third quartile, for health points, attack, defense, special attack, special defense, and speed stastics by type of Pokemon.

The median, first quartile, and 3rd quartile for Health Points for Bug type Pokemon are `r gtsummary::inline_text(table1, variable = HP, column = Bug)`

## Creating regression table of HP by Attack, Defense, Special Attack, Special Defense, and speed

```{r}
gtsummary::tbl_uvregression(
								 pokemon,
								 y = HP,
								 include = c(HP, Attack, Defense, Sp..Atk, Sp..Def, Speed),
								 label = list(
														 	HP = "Health Points",
														 	Sp..Atk = "Special Attack",
														 	Sp..Def = "Special Defense"),
								 method = lm
								 )
```

Univariate regression table depicting number, Beta statistic, 95% CI, and p-value for Health Points

## Creating a Histogram for HP of all Pokemon in the dataset

```{r}
hist(pokemon$HP)
```

Histogram depicting the frequency of specific Health Point ranges for all Pokemon in the dataset

## Creating function to return mean value for continuous variables

```{r}
variable_mean <- function(x){
							val = sum(x)/length(x)		
							return(val)
							}
variable_mean(pokemon$Attack)
```

## 
